Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains

### 2015-02-17 latex-style-files-spie-manuscript/manuscript_snellendo.tex
- added pics for dc controller and axis - shuffled data pic

	%\begin{figure}
   %\begin{center}
   %\begin{tabular}{c}
   %\includegraphics[height=16cm]{LSMdata.eps}
   %\end{tabular}
   %\end{center}
   %\caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective). (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm. (C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = 100 µm.} 
   %\end{figure}
	%
	%Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.

@@

%\listoftables

\section{Supplementary information}

>>>>

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{data_panel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective. (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$. (C,D,E) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = $100 \micro m$.} 
   \end{figure}

	To exemplify the imaging capabilities of our microscope see Fig. \ref{fig:LSMdata}.

@@

%\listoftables
\pagebreak
\section{Supplementary information}
